### 2020-06-30 paper/sex_selection_spacing-ver4.tex
Reorganize spacing sections (#12)
* Combine spacing sections and add a summary of answer to main question

* Explain reorganized spacing section in the response letter

In the second group are women who use sex selection and who, therefore, show the expected 
associated increase in birth intervals for those sex compositions. 
However, the intervals for their other sex compositions have increased even more. 
The result is that the relative pattern remains more or less the same. 
An example of this group is women with eight more years of education in the second spell.

The final group consists of those women, who, in the absence of a son, have the most 
biased sex ratios and the longest birth intervals, and where this spacing is longer than 
for the other possible sex compositions. 
The most extreme example is best-educated urban women with two girls with a sex ratio 
approaching 80 and an average birth interval of 42 months. 
This birth interval is seven months longer than with at least one boy.

In summary, although birth spacing has increased over time with improving economic 
conditions and falling fertility, it is clear that most of the increases in birth spacing 
come from the increased use of sex selection. 
The most substantial increase over the four decades is a full year for the best-educated 
women with two girls.

>>>>

In the second group are women who use sex selection and who, therefore, show the expected 
associated increase in birth intervals for those sex compositions. 
However, the intervals for their other sex compositions have increased even more. 
The result is that the relative pattern remains more or less the same. 
An example is women with eight more years of education in the second spell.

The final group consists of those women, who, in the absence of a son, have the most 
biased sex ratios and the longest birth intervals, and where this spacing is longer than 
for the other possible sex compositions. 
The most extreme example is best-educated urban women with two girls, who have a sex ratio 
approaching 80 and an average birth interval of 42 months. 
This birth interval is seven months longer than with at least one boy.

In summary, although birth spacing has increased over time with improving economic 
conditions and falling fertility, most of the increases in birth spacing come from the
increased use of sex selection. 
The most substantial increase over the four decades is a full year for the best-educated 
women with two girls, which is the group with the most biased sex ratio.
